### 2019-08-14 thesis.tex
very close to the end

The theory developed during this graduate research analyses the combined
action of nonlinear kinetic instabilities and collisional processes in
the context of solar physics. To contextualize our work within the solar
plasma research, in this appendix, we present a brief review of the
current state-of-art of solar and space physics research, followed by a
discussion on the solar plasma phenomena related to our study.

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity in
the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the
solar system and extends for approximately $140\unit{AU}$\footnote{An AU
  (astronomical unit) is defined as the mean distance between the Sun and
  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
galactic space. Its outer limit is the \emph{heliopause}, an interface zone
where the outgoing pressure of the solar plasma balances the incoming pressure
from the interstellar medium. This comet-shaped plasma bubble \cite{Dialynas2017},
has an inner boundary, the \emph{termination shock}, which delimits the sphere
of absolute influence of the solar plasma. Beyond the termination shock, at
roughly $100\unit{AU}$ from the Sun, extending out to the heliopause, is the
\emph{heliosheath}. In this region, the solar wind particles start being subjected
to increasing external pressure, transitioning to a subsonic, turbulent flow that
blends and interacts directly with the matter in the local interstellar medium
\cite{NAP13060}. In \autoref{figD1}, we have a depiction of the regions and
boundaries described above, and the current location of both Voyager missions,
that are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

The ultimate goal of heliophysics can be summarized as the search for a
better understanding of the solar dynamics and how it affects the Earth,
other planetary bodies, and the interstellar medium. The heliosphere is
a coupled system, where different interacting elements that might look
unrelated at first sight are connected by underlying plasma processes
\cite{NAP13060}. A great example of this interconnection is the relation
between the appearance of sunspots and the occurrence of non-recurrent
geomagnetic storms, which are the most intense space weather disturbances.
Evidence of such relationship started to appear at the end of the $19$th
century. The correct hypothesis (coronal mass ejections associated with
solar flares), however, which depended on advances in plasma physics
theory, came along only in $1929$ \cite{chapman1929cosmical,Koskinen2011}.

A better comprehension of the Sun and the dynamic space around our planet
goes beyond the pure scientific curiosity. It is true that this accessible
space physics laboratory can lead to discoveries that can be applied and
extended to remote cosmic systems. But the primary reason behind the
international effort (see Figures \ref{nasa} and \ref{esa}) on understanding
the complex physics of the Sun and the interplanetary space, is to enable
means to predict the occurrence and intensity of solar activity. This may
open the possibility of developing reliable space-weather forecasts that
may help us to protect satellites, humans

\begin{itemize}
\item The magnetic dynamo processes involved in the generation and variability
  of magnetic fields in the Sun, and how it determines the dynamics of the
  11-year solar cycle of solar activity \cite{Charbonneau2005};
\item The role of magnetic reconnection in the coronal mass ejection process
  \cite{Qiu2005};
\item The coronal heating problem \cite{Vinas2000,PP14,Pezzi2017};
\item   
\end{itemize}

Figures
\ref{nasa} and \ref{esa} illustrate the current space missions of NASA and the
European Space Agency (ESA), respectively. Describing the processes assessed by
each one of the illustrated probes it is out of the scope of this work\footnote{
  For a complete description, of the NASA missions is available at
\url{https://science.nasa.gov/missions-page?field_division_tid=5&field_phase_tid=All}.
For the ESA missions, go to \url{http://sci.esa.int/home/51459-missions/}.
  Both sites were accessed at 11/08/2019.}.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{hso_fleet_chart_april_2019.pdf}
    \caption{NASA's present and future heliophysics system observatory. The number
      between parenthesis under the probe's name is the total number of spacecrafts
      that compose the mission.}
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics}
      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
    \label{nasa}
  \end{center}
\end{figure}
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
    \caption{ESA's past, present, and future science missions for studying the solar system.}
      {\footnotesize Credit:}
      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
    \label{esa}
  \end{center}
\end{figure}
% As described above, ionized particles ejected by the Sun determine the
% overall dynamics of the interplanetary medium until the termination shock
% boundary. Beyond this limit, the solar wind still has a significant
% influence on the nature of the local interstellar space for a long distance
% up to the heliopause.
% As a well established scientific discipline, solar and space physics work
% towards developing a better comprehension of the Sun and
% the solar processes molding this vast and complex dynamic system called
% heliosphere.

% ; where, within, very close to its most influential object,
% lies our home planet - Earth.

\subsection{The Sun and its effects on the near-Earth environment}
\label{sec:sun}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{corona2017.png}
    %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{corona}
  \end{center}
\end{figure}

>>>>

The theory developed during this graduate research analyses the combined
action of nonlinear kinetic instabilities and collisional processes in
the context of solar physics. To contextualize our work within the solar
plasma research, in this appendix, we present a brief review of the
current state-of-the-art of solar and space physics research, followed
by a discussion on the solar plasma phenomena related to our study.

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity
in the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the
solar system and extends for approximately $140\unit{AU}$\footnote{An AU
  (astronomical unit) is defined as the mean distance between the Sun and
  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
galactic space. Its outer limit is the \emph{heliopause}, an interface
zone where the outgoing pressure of the solar plasma balances the incoming
pressure from the interstellar medium. This comet-shaped plasma bubble
\cite{Dialynas2017}, also has an inner boundary, the \emph{termination shock},
which delimits the sphere of absolute influence of the solar plasma. Beyond
the termination shock, at roughly $100\unit{AU}$ from the Sun, extending
out to the heliopause, lies the \emph{heliosheath}. In this region, the
solar wind particles start being subjected to increasing external pressure,
transitioning to a subsonic, turbulent flow that blends and interacts
directly with the matter in the local interstellar medium \cite{NAP13060}.
In \autoref{figD1}, we have a depiction of the regions and boundaries
described above, and the current location of both Voyager missions, that
are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.89\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

The ultimate goal of heliophysics can be summarized as the search for a
better understanding of the solar dynamics and how it affects the Earth,
other planetary bodies, and the interstellar medium. The heliosphere is
a coupled system, where different interacting elements that might look
unrelated at first sight are connected by underlying plasma processes
\cite{NAP13060}. A great example of this interconnection is the relation
between the appearance of sunspots and the occurrence of non-recurrent
geomagnetic storms, which are the most intense space weather disturbances.
Evidence of such relationship started to appear at the end of the $19$th
century. However, the correct hypothesis supporting this correlation
(coronal mass ejections associated with solar flares), which depended
on advances in plasma physics theory, came along only in $1929$
\cite{chapman1929cosmical,Koskinen2011}.

\subsection{The Sun and the near-Earth environment}
\label{sec:sun}
A better comprehension of the Sun and the dynamic space around our planet
goes beyond the pure scientific curiosity. This accessible space physics
laboratory can indeed lead to discoveries that can be applied and extended
to remote cosmic systems. However, the primary reason behind the international
effort\footnote{A complete description, of NASA's missions is available at
\url{https://science.nasa.gov/missions-page?field_division_tid=5&field_phase_tid=All}.
For ESA's missions, go to \url{http://sci.esa.int/home/51459-missions/}.
Both websites were accessed at 11/08/2019.} (see Figures \ref{nasa} and \ref{esa}
) on understanding the complex physics of the Sun and interplanetary space
is to unlock means of predicting the occurrence and intensity of solar activity,
and anticipate how the near-Earth environment will be affected.  On that regard,
a critical aspect being addressed is the response of Earth’s magnetosphere,
ionosphere, and atmosphere to solar inputs. The objective is to open the
possibility of developing reliable models for the space weather forecast.
Forecasting space weather may help us to protect humans and electronic equipment
in space from the incoming flux of energetic ionized matter and radiation coming
from the Sun, and ground-based technological infrastructure from the geomagnetic
storms they cause \cite{NAP13060}.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.89\textwidth]{hso_fleet_chart_april_2019.pdf}
    \caption{NASA's present and future heliophysics system observatory. The number
      between parenthesis under the probe's name is the total number of spacecrafts
      that compose the mission.}
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics}
      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
    \label{nasa}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.89\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
    \caption{ESA's past, present, and future science missions for studying the solar system.}
      {\footnotesize Credit:}
      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
    \label{esa}
  \end{center}
\end{figure}

Another important aspect... blah blah blah whiskas sachet... solar corona.
Talk about my work then corro pra galera

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.89\textwidth]{corona2017.png}
    %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{corona}
  \end{center}
\end{figure}
